\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-05-11 doc/paper.tex
better spacing of listings

\documentclass[final,3p,11pt,pdflatex]{elsarticle}
\usepackage[utf8x]{inputenc}      % input font encoding
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}          % output font encoding
\usepackage{booktabs,tabularx}
\usepackage{rotating}             % for sidewaystable
\usepackage{xspace}
\usepackage[usenames]{xcolor}
\usepackage{tikz,tikz-uml}
\usepackage{listings}
\bibstyle{elsarticle-num}
% source code highlighting
\lstset{breaklines=true,
  breakatwhitespace=true,
  stepnumber=1,
  basicstyle=\ttfamily\footnotesize,
  commentstyle=\ttfamily\color{gray},
  prebreak={\textbackslash},
  breakindent=10pt,
  breakautoindent=false,
  showspaces=false,
  showstringspaces=false,
  frame=single}
\usepackage[pdftitle={FlexibleSUSY --- A spectrum generator generator for supersymmetric models},
pdfauthor={Peter Athron,Jae-hyeon Park,Dominik Stockinger,Alexander Voigt},
pdfkeywords={FlexibleSUSY,supersymmetry,spectrum,generator,MSSM,NMSSM,E6SSM},
bookmarks=true, linktocpage]{hyperref}

>>>>

\documentclass[final,3p,11pt,pdflatex]{elsarticle}
\usepackage[utf8x]{inputenc}      % input font encoding
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}          % output font encoding
\usepackage{booktabs,tabularx}
\usepackage{rotating}             % for sidewaystable
\usepackage{xspace}
\usepackage[usenames]{xcolor}
\usepackage{tikz,tikz-uml}
\usepackage{listings}
\bibstyle{elsarticle-num}
% source code highlighting
\lstset{breaklines=true,
  breakatwhitespace=true,
  stepnumber=1,
  basicstyle=\ttfamily\footnotesize,
  commentstyle=\ttfamily\color{gray},
  prebreak={\textbackslash},
  breakindent=10pt,
  breakautoindent=false,
  showspaces=false,
  showstringspaces=false,
  frame=single,
  abovecaptionskip=0em,
  aboveskip=1.5em,
  belowcaptionskip=0.5em,
  belowskip=1em,
}
\usepackage[pdftitle={FlexibleSUSY --- A spectrum generator generator for supersymmetric models},
pdfauthor={Peter Athron,Jae-hyeon Park,Dominik Stockinger,Alexander Voigt},
pdfkeywords={FlexibleSUSY,supersymmetry,spectrum,generator,MSSM,NMSSM,E6SSM},
bookmarks=true, linktocpage]{hyperref}
